---
title: "Newspapers in Times of Low Advertising Revenues"
author: "Zikun (Alex) Xu"
date: "12/22/2020"
output: pdf_document
---


```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Apply libraries that are used in this paper
library(tidyverse)
library(broom)
library(here)
library(here)
library(haven)
library(huxtable)
library(scales)
library(tidyverse)

```

#Abstract




#Introduction






#Data

*Paraphrase
(The) dataset contains annual data on local and national newspapers between 1960 and 1974, as well as detailed information on television content. In 1967, the French government announced it would relax long-standing regulations that prohibited television advertising. We provide evidence that this reform can be plausibly interpreted as an exogenous and negative shock to the advertising side of the newspaper industry… [I]t is likely that the introduction of television advertising constituted a direct shock to the advertising side of the newspaper industry and only an indirect shock to the reader side… (O)ur empirical setting constitutes a unique opportunity to isolate the consequences of a decrease in newspapers’ advertising revenues on their choices regarding the size of their newsroom, the amount of information to produce, and the prices they charge to both sides of the market.

\begin{tabular}{l*{1}{cccccc}}
\hline\hline
                    &\multicolumn{6}{c}{}                                                         \\
                    &        Mean&      Median&          sd&         Min&         Max&         Obs\\
\hline
\textbf{Prices}     &            &            &            &            &            &            \\
Unit buyer price    &         3.6&         3.5&         1.3&         2.4&         9.3&         152\\
Subscription price per issue&         2.8&         2.7&         0.7&         1.9&         5.6&         148\\
Display ad rate (listed price)&       121.1&       114.5&        81.0&        17.5&       274.2&         121\\
\textbf{Revenues \& journalists}&            &            &            &            &            &            \\
Total revenues (million \euro)&         425&         271&         403&          19&        1482&         162\\
Revenues from advertising (million \euro)&         228&         103&         258&           7&         864&         161\\
Revenues from sales (million \euro)&         199&         145&         181&          12&         657&         162\\
Share of advertising in total revenues (\%)&        47.4&        51.1&        21.3&         8.0&        81.0&         162\\
Number of journalists&         117&          85&          81&          21&         326&         158\\
\textbf{Circulation}&            &            &            &            &            &            \\
Total circulation   &     295,210&     181,574&     292,838&      16,112&   1,143,676&         162\\
Share of subscribers (\%)&        25.6&        18.5&        26.3&         0.7&        92.3&         163\\
\textbf{Content}    &            &            &            &            &            &            \\
Number of pages     &          19&          17&           7&           8&          38&         138\\
News hole (nonadvertising space)&          13&          13&           4&           6&          25&         138\\
Advertising space   &           5&           4&           4&           0&          16&         138\\
\hline\hline
\end{tabular}



```{r data}
#Read the dta file, similar to read_csv()
newspapers <- read_dta(here::here("Angelucci_Cage_AEJMicro_dataset.dta"))

#Filter out to only use the variables we need
newspapers_filtered <- 
  newspapers %>% 
  dplyr::select(year, id_news, after_national, local, national, # Diff in diff variables
         ra_cst, qtotal, ads_p4_cst, ads_s, # Advertising side dependents
         ps_cst, po_cst, qtotal, qs_s, rs_cst) %>% #Reader side dependents
  mutate(ra_cst_div_qtotal = ra_cst / qtotal) %>% # An advertising side dependents needs to be built
  mutate_at(vars(id_news, after_national, local, national), ~as.factor(.)) %>% # Change some to factors
  mutate(year = as.integer(year))
newspapers_filtered
```



```{r}

#Shows the revenues of Local and National newspaper companies of these years
newspapers %>% 
  mutate(type = if_else(local == 1, "Local", "National")) %>% 
  ggplot(aes(x = year, y = ra_cst)) +
  geom_point(alpha = 0.5) +
  scale_y_continuous(labels = dollar_format(prefix="$", suffix = "M", scale = 0.000001)) +
  labs(x = "Year",
       y = "Advertising revenue") +
  facet_wrap(vars(type),
               nrow = 2) +
  theme_classic() +
  geom_vline(xintercept = 1966.5, linetype = "dashed")

```


#Model

##Model for Advertising side
```{r}
# Advertising side
ad_revenue <- lm(log(ra_cst) ~ after_national + id_news + year, data = newspapers_filtered)
#Revenue affected by 
#summary(ad_revenue)
ad_revenue_div_circulation <- lm(log(ra_cst_div_qtotal) ~ after_national + id_news + year, data = newspapers_filtered)
ad_price <- lm(log(ads_p4_cst) ~ after_national + id_news + year, data = newspapers_filtered)
ad_space <- lm(log(ads_s) ~ after_national + id_news + year, data = newspapers_filtered)


#This removes 
omit_me <- c("(Intercept)", "id_news3", "id_news6", "id_news7", "id_news13", 
             "id_news16", "id_news25", "id_news28", "id_news34", "id_news38", 
             "id_news44", "id_news48", "id_news51", "id_news53", "id_news54", 
             "id_news57", "id_news60", "id_news62", "id_news66", "id_news67", 
             "id_news70", "id_news71", "id_news72", "id_news80", "id_news82", 
             "id_news88", "id_news95", "id_news97", "id_news98", "id_news103", 
             "id_news105", "id_news106", "id_news118", "id_news119", "id_news127", 
             "id_news136", "id_news138", "id_news148", "id_news151", "id_news153", 
             "id_news154", "id_news157", "id_news158", "id_news161", "id_news163", 
             "id_news167", "id_news169", "id_news179", "id_news184", "id_news185", 
             "id_news187", "id_news196", "id_news206", "id_news210", "id_news212", 
             "id_news213", "id_news224", "id_news225", "id_news234", "id_news236", 
             "id_news245", "id_news247", "id_news310", "id_news452", "id_news467", 
             "id_news469", "id_news480", "id_news20040", "id_news20345", 
             "id_news20346", "id_news20347", "id_news20352", "id_news20354", 
             "id_news21006", "id_news21025", "id_news21173", "id_news21176", 
             "id_news33718", "id_news34689", "id_news73")

huxreg("Ad. rev." = ad_revenue, 
       "Ad rev. div. circ." = ad_revenue_div_circulation, 
       "Ad price" = ad_price, 
       "Ad space" = ad_space,
        omit_coefs = omit_me, 
        number_format = 2
        )

```


```{r}

# Consumer side
subscription_price <- lm(log(ps_cst) ~ after_national + id_news + year, data = newspapers_filtered)
unit_price <- lm(log(po_cst) ~ after_national + id_news + year, data = newspapers_filtered)
circulation <- lm(log(qtotal) ~ after_national + id_news + year, data = newspapers_filtered)
share_of_sub <- lm(log(qs_s) ~ after_national + id_news + year, data = newspapers_filtered)
revenue_from_sales <- lm(log(rs_cst) ~ after_national + id_news + year, data = newspapers_filtered)

omit_me <- c("(Intercept)", "id_news3", "id_news6", "id_news7", "id_news13", 
             "id_news16", "id_news25", "id_news28", "id_news34", "id_news38", 
             "id_news44", "id_news48", "id_news51", "id_news53", "id_news54", 
             "id_news57", "id_news60", "id_news62", "id_news66", "id_news67", 
             "id_news70", "id_news71", "id_news72", "id_news80", "id_news82", 
             "id_news88", "id_news95", "id_news97", "id_news98", "id_news103", 
             "id_news105", "id_news106", "id_news118", "id_news119", "id_news127", 
             "id_news136", "id_news138", "id_news148", "id_news151", "id_news153", 
             "id_news154", "id_news157", "id_news158", "id_news161", "id_news163", 
             "id_news167", "id_news169", "id_news179", "id_news184", "id_news185", 
             "id_news187", "id_news196", "id_news206", "id_news210", "id_news212", 
             "id_news213", "id_news224", "id_news225", "id_news234", "id_news236", 
             "id_news245", "id_news247", "id_news310", "id_news452", "id_news467", 
             "id_news469", "id_news480", "id_news20040", "id_news20345", 
             "id_news20346", "id_news20347", "id_news20352", "id_news20354", 
             "id_news21006", "id_news21025", "id_news21173", "id_news21176", 
             "id_news33718", "id_news34689", "id_news73")

huxreg("Subscription price" = subscription_price, 
       "Unit price" = unit_price, 
       "Circulation" = circulation, 
       "Share of sub" = share_of_sub,
       "Revenue from sales" = revenue_from_sales,
       omit_coefs = omit_me, 
       number_format = 2
       )

```










# References


- Canadian Demographics at a Glance. (2014). Statistics Canada. Catalogue no. 91-003-X.

- R Core Team (2020). R: A language and environment for statistical
  computing. R Foundation for Statistical Computing, Vienna, Austria.
  URL https://www.R-project.org/.